Protoype for metaanalysis

### 2018-09-18 scripts/2018.09.19-meta_analysis_prototype.Rmd
Creating a new meta-analysis Rmd

---
title: "Dataset Summary"
author: "Daniel Falster"
date: "06/07/2018"
output: 
  html_document:
    fig_height: 6
    fig_width: 10
    df_print: paged
    rows.print: 10
    code_folding: hide
    theme: yeti
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
library(readr)
library(dplyr)
library(metafor)

@@

Load data
```{r cars}
data_raw <- load_raw("data/dr7.0_all_control_data.csv") 
```

Clean data & define population variable
```{r}
data <- clean_raw_data(data_raw) %>%
  mutate(population = sprintf("%s-%s", production_center, strain_name))
```

Export copy of data for body size analysis
```{r}
dir.create("export", F, F)
data %>% filter(parameter_name == "body weight") %>%
  saveRDS("export/body_weight.rds")
```

Create a copy of data for variance analysis

```{r}
data_par_age <- data_subset_parameter_individual_by_age(data, "body weight", age_min = 98, age_center = 100)
```

>>>>

---
title: "Protoype for metaanalysis"
author: "Daniel Falster & Alistair Senior + Shinichi messing things up"
date: "03/07/2018"
output: 
  html_document:
    fig_height: 6
    fig_width: 10
    df_print: paged
    rows.print: 10
    code_folding: show
    theme: yeti
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=TRUE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE, cache=FALSE)
knitr::opts_knit$set(root.dir =  rprojroot::find_root("README.md"))
```

```{r}
library(readr)
library(dplyr)
library(metafor)

@@

Load data & clean data

```{r, eval = FALSE}
# Load raw data - save cleaned dataset as RDS for reuse
data_raw <- load_raw("data/dr7.0_all_control_data.csv") %>%
    clean_raw_data()
dir.create("export", F, F)
saveRDS(data_raw, "export/data_clean.rds")
```

```{r}
data <- readRDS("export/data_clean.rds")
```

Define population variable
```{r}
data <- data %>%
  mutate(population = sprintf("%s-%s", production_center, strain_name))
```

Create a copy of data for variance analysis
```{r}
data_par_age <- data_subset_parameter_individual_by_age(data, "body weight", age_min = 98, age_center = 100)
```
